---
title: "data prep"
author: "hannah hess"
date: "November 29, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stargazer)
library(gtrendsR)
library(tidyverse)
library(knitr)
library(readxl)


```

This is a page for where I download, compile and clean the data set that will be used in my rpubs. 


```{r, include=FALSE}
#grabbing country level data in 
#for a discussion of how I chose terms please consult microsoft spreadsheet

#grabbing data for EG, SA, JO, MA 
grab1 <- gtrends(keyword = c("sex"), geo = c("EG", "SA", "AE","JO", "MA"), time = "today+5-y")
grab2 <- gtrends(keyword = c("porn"), geo = c("EG", "SA", "AE","JO", "MA"), time = "today+5-y")


#merging grabbed data and averaging porn search terms for grabs 1 and 2 

grab2 <- grab2$interest_over_time %>% 
  select(hits, date, geo) %>% 
  transmute(hits.porn = hits, date = date, geo = geo)
  

grab1 <- grab1$interest_over_time %>% 
  rename(hits.sex = hits) %>% 
  left_join(grab2, by = c("date", "geo")) %>% 
  mutate(sum = (hits.sex + hits.porn)/2)

rm(grab2)
#we're left with grab 1! 

#gabbing data for Iran, Afghanistan,
#first term is same across countries
grab4 <- gtrends(keyword = c("sex"), geo = c("IR", "AF"), time = "today+5-y")
grab3 <- gtrends(keyword = c("سکس"), geo = c("IR", "AF"), time = "today+5-y")

#merging grabbed data and averaging porn search terms for grabs 3 and 4
#renaming the sks term to hits.porn for the purpose of binding rows
grab3 <- grab3$interest_over_time %>% 
  select(hits, date, geo) %>% 
  transmute(hits.porn = hits, date = date, geo = geo)
  

grab4 <- grab4$interest_over_time %>% 
  rename(hits.sex = hits) %>% 
  left_join(grab3, by = c("date", "geo")) %>% 
  mutate(sum = (hits.sex + hits.porn)/2)

rm(grab3)
#we're left with grab 4!

#grabbing data for Turkey, Pakistan
grab5 <- gtrends(keyword = c("sex"), geo = c("PK", "TR", "TN", "LY"), time = "today+5-y")
grab6 <- gtrends(keyword = c("porn"), geo = c("PK", "TR", "TN", "LY"), time = "today+5-y")
grab5 <- grab5$interest_over_time %>% 
  select(hits, date, geo) %>% 
  transmute(hits.sex = hits, date = date, geo = geo)
  

grab6 <- grab6$interest_over_time %>% 
  rename(hits.porn = hits) %>% 
  left_join(grab5, by = c("date", "geo")) %>% 
  mutate(sum = (hits.sex + hits.porn)/2)

#we're left with grab 6
rm(grab5)


#bind rows from grabbed frames and label it D1_interest

D1_interest <- bind_rows(grab1, grab4, grab6)



```

```{r, cache = TRUE, include = FALSE, echo = FALSE, message = FALSE, warning= FALSE}


#load the data set I made with dates of ramadan and major holidays in order to create a variable indicating the presence of absence of ramadan

ramadan_dates <- read_excel("ramadan_dates.xlsx")


```


The table below shows related queries for searches in the category of sex and porn over Ramadan. Two demonstrate the nature of the searches I display the top 10 related search values. Warning, this includes graphic content.
According to the google trends website, scoring is on a relative scale where a value of 100 is the most commonly searched query, 50 is a query searched half as often as the most popular query, and so on.
  
```{r, cache = TRUE, echo = FALSE, message = FALSE, warning= FALSE}
#showing/determining high volume porn searches 


#justify that I'm picking the right terms (warning explicit content) - since I'm focused with change over time - its not critical that I isolate all the relevant terms but just that they indeed be pornography serach terms  and that they capture a high level of the variation over time
#related queries captures the following: 
# Users searching for your term also searched for these queries. You can sort by the following metrics:
# * Top - The most popular search queries. Scoring is on a relative scale where a value of 100 is the most commonly searched query, 50 is a query searched half as often as the most popular query, and so on.
#   
# D1$related_queries %>% 
#      select(subject, value) %>% 
#       slice(1:7) %>% 
#      kable(caption = "A Table of Related Queries", col.names = c("Correlation Score", "Value"))
# 
# D2$related_queries %>% 
#   select(subject, value) %>% 
#   slice(1:7) %>% 
#   kable(caption = "A Table of Related Queries", col.names = c("Correlation Score", "Value"))



```


```{r, cache = TRUE, include = FALSE, echo = FALSE, message = FALSE, warning= FALSE}


#I have a problem: the gtrends data set does not indicate the presence or absence of Ramadan. I have to pull that info from a different data set I have called ramadan_holiday
#My google trends data set (D1_interest) includes ramadan search values for a whole week 
#manipulate data set to add all days of the week 
D1_interest$date1 = as.Date(D1_interest$date) + 1 
D1_interest$date2 = as.Date(D1_interest$date) + 2 
D1_interest$date3 = as.Date(D1_interest$date) + 3 
D1_interest$date4 = as.Date(D1_interest$date) + 4 
D1_interest$date5 = as.Date(D1_interest$date) + 5 
D1_interest$date6 = as.Date(D1_interest$date) + 6 

D1_interest$year <- substring(D1_interest$date,1,4)


#For loop to create (1) a "days_in_ram" variable ->  the number of days in a given week with ramadan present and also (2) "in_ram" variable -> (0 or 1) whether or not ramadan is present in that week
#first iterate over a week in a given year in the D1_interests data set to see if there are any matches for Ramadan occuring
#count the number of days of a given week in teh D1_interest$date variable which overlap with ramadan
#create a binary variable to code 1 if a week includes more than 3 days of ramadan. 

for (i in 1:length(D1_interest$date)) {
  D1_interest[i, "days_in_ram"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (D1_interest[i, j] >= ramadan_dates[ramadan_dates$year==   D1_interest[i, "year"]   &  ramadan_dates$Holiday == "Ramadan" , ]$start  ) & (D1_interest[i, j] <= ramadan_dates[ramadan_dates$year== D1_interest[i,"year"] & ramadan_dates$Holiday == "Ramadan" ,]$end  ) ) {
        D1_interest[i, "days_in_ram"] =   D1_interest[i, "days_in_ram"]  + 1
    }
  }
  
  if (D1_interest[i, "days_in_ram"] > 2){
      D1_interest[i,"in_ram"] = 1
  } else{
      D1_interest[i,"in_ram"] = 0
  }
  
  
}


#code variable for the week before ramadan to test whether the week before ramadan results in a change in values

D1_interest$before_ram = 0 
  for (i in 1:length(D1_interest$date) - 1) {
if (D1_interest$in_ram == 0 & D1_interest$in_ram[i +1] == 1) D1_interest$before_ram[i] = 1 else D1_interest$before_ram[i] <- 0
}

# Next I code a variable for 2 weeks before ramadan to test whether 2 weeks before ramadan results in a change in values
# this might be useful for future but I'm placing this on the side for the present because I don't have room to discuss 

# D1_interest$before2_ram = 0 
#   for (i in 1:length(D1_interest$date) - 2) {
# if (D1_interest$in_ram == 0 & D1_interest$in_ram[i +2] == 1) D1_interest$before2_ram[i] = 1 else D1_interest$before2_ram[i] <- 0
# }


#Thank you to Eric Wasserman Harvard 2019 Dunster House for helping me conceptualize how best to approach the coding problem above!




#repeat the ramadan iteration but this time for celebratory holidays
#code variable for celebratory holidays, same method as ramadan 


for (i in 1:length(D1_interest$date)) {
  D1_interest[i, "days_in_eid"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (D1_interest[i, j] >= ramadan_dates[ramadan_dates$year==   D1_interest[i, "year"]   &  ramadan_dates$Holiday ==  "Eid al-Fitr" , ]$start  ) & (D1_interest[i, j] <=  ramadan_dates[ramadan_dates$year== D1_interest[i,"year"] & ramadan_dates$Holiday ==  "Eid al-Fitr" ,]$end  ) ) {
        D1_interest[i, "days_in_eid"] =   D1_interest[i, "days_in_eid"]  + 1
    }
  }
    if (D1_interest[i, "days_in_eid"] > 2){
      D1_interest[i,"in_eid"] = 1
  } else{
      D1_interest[i,"in_eid"] = 0
  }
  

}







#I'm commenting out this section for coding in Eid al-ahda which occurs later in the calender year because I didn't find any significant relationship
#however, in the future I could use the fact taht Eid al-ahda isn't signficiant  to better explain the Eid al-futr effect rule out the "holida"
# for (i in 1:length(D1_interest$date)) {
#   D1_interest[i, "days_in_eida"] = 0 
#   for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
#     if ( (D1_interest[i, j] >= ramadan_dates[ramadan_dates$year==   D1_interest[i, "year"]   &  ramadan_dates$Holiday ==  "Eid-al-adha" , ]$start  ) & (D1_interest[i, j] <=  ramadan_dates[ramadan_dates$year== D1_interest[i,"year"] & ramadan_dates$Holiday ==  "Eid-al-adha" ,]$end  ) ) {
#         D1_interest[i, "days_in_eida"] =   D1_interest[i, "days_in_eida"]  + 1
#     }
#   }
# 
#   
# }
 

#write an rds file to save the data and graph in presentation
write_rds(D1_interest, "D1_interest.rds")


```




```{r, cache = TRUE, include = FALSE, echo = FALSE, message = FALSE, warning= FALSE}

#repeat the above step but for WORLD data to test if there's a global impact


#download world data to see if theres a world influence, the default is world data unless you change something
world <- gtrends(keyword = "sex", time = "today+5-y")
world2 <- gtrends(keyword = "porn", time = "today+5-y")

world2 <- world2$interest_over_time %>% 
  select(hits, date, geo) %>% 
  transmute(hits_porn = hits, date = date, geo = geo)

world_interest <- world$interest_over_time %>% 
  rename(hits_sex = hits) %>% 
  left_join(world2, by = c("date", "geo")) %>% 
  mutate(sum = (hits_sex + hits_porn)/2)


#I have a problem: the gtrends data set does not indicate the presence or absence of Ramadan. I have to pull that info from a different data set I have called ramadan_holiday
#My google trends data set (D1_interest) includes ramadan search values for a whole week 
#manipulate data set to add all days of the week 
world_interest$date1 = as.Date(world_interest$date) + 1 
world_interest$date2 = as.Date(world_interest$date) + 2 
world_interest$date3 = as.Date(world_interest$date) + 3 
world_interest$date4 = as.Date(world_interest$date) + 4 
world_interest$date5 = as.Date(world_interest$date) + 5 
world_interest$date6 = as.Date(world_interest$date) + 6 

world_interest$year <- substring(world_interest$date,1,4)


#For loop to create (1) a "days_in_ram" variable ->  the number of days in a given week with ramadan present and also (2) "in_ram" variable -> (0 or 1) whether or not ramadan is present in that week
#first iterate over a week in a given year in the D1_interests data set to see if there are any matches for Ramadan occuring
#count the number of days of a given week in teh D1_interest$date variable which overlap with ramadan
#create a binary variable to code 1 if a week includes more than 3 days of ramadan. 

for (i in 1:length(world_interest$date)) {
  world_interest[i, "days_in_ram"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (world_interest[i, j] > ramadan_dates[ramadan_dates$year==   world_interest[i, "year"]   &  ramadan_dates$Holiday == "Ramadan" , ]$start  ) & (world_interest[i, j] < ramadan_dates[ramadan_dates$year== world_interest[i,"year"] & ramadan_dates$Holiday == "Ramadan" ,]$end  ) ) {
        world_interest[i, "days_in_ram"] =   world_interest[i, "days_in_ram"]  + 1
    }
  }
  
  if (world_interest[i, "days_in_ram"] > 2){
      world_interest[i,"in_ram"] = 1
  } else{
      world_interest[i,"in_ram"] = 0
  }
  
  
}

#same code as above - Eid al-fitr: days_in_eid

for (i in 1:length(world_interest$date)) {
  world_interest[i, "days_in_eid"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (D1_interest[i, j] >= ramadan_dates[ramadan_dates$year==   D1_interest[i, "year"]   &  ramadan_dates$Holiday ==  "Eid al-Fitr" , ]$start  ) & (D1_interest[i, j] <=  ramadan_dates[ramadan_dates$year== world_interest[i,"year"] & ramadan_dates$Holiday ==  "Eid al-Fitr" ,]$end  ) ) {
        world_interest[i, "days_in_eid"] =   world_interest[i, "days_in_eid"]  + 1
    }
  }
   if (D1_interest[i, "days_in_eid"] > 2){
      D1_interest[i,"in_eid"] = 1
  } else{
      D1_interest[i,"in_eid"] = 0
  }

}

#code for the week before ramadan

for (i in 1:length(world_interest$date)) {
  D1_interest[i, "days_before"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (D1_interest[i, j] >= ramadan_dates[ramadan_dates$year==   D1_interest[i, "year"]   &  ramadan_dates$Holiday == "Ramadan" , ]$start  ) & (D1_interest[i, j] <= ramadan_dates[ramadan_dates$year== D1_interest[i,"year"] & ramadan_dates$Holiday == "Ramadan" ,]$end  ) ) {
        D1_interest[i, "days_in_ram"] =   D1_interest[i, "days_in_ram"]  + 1
    }
  }
  
  if (D1_interest[i, "days_in_ram"] > 2){
      D1_interest[i,"in_ram"] = 1
  } else{
      D1_interest[i,"in_ram"] = 0
  }
  
  
}

#write rds to use in second portion 
write_rds(world_interest, "world.rds")

```





