---
title: "regression analysis"
author: "hannah hess"
date: "November 29, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stargazer)
library(gtrendsR)
library(tidyverse)
library(knitr)
library(readxl)
#library(ls)


```

This is a page for regression analysis, tables and charts
in another page, I will look at graphs of - popular hours for porn consumption, changes in porn consumption over time

 
first - try to pull a cross country data frame from google then combine by country... although I could make life easy on myself and not pull more than two countries. 
```{r, cache = TRUE, include = FALSE, echo = FALSE, message = FALSE, warning= FALSE}

#create preliminary data set from gtrends - last 5 years. Although I would have ideally liked to gather data from more than 5 years - I'm limited in scope because the algorithm can't pull more data then that at a time




  #download data for sex and porn searches, this has to be done seperately or there's an overload issue
D1 <- gtrends(keyword = c("sex"), geo = c("EG", "SA", "AE","JO", "MA"), time = "today+5-y")
D2 <- gtrends(keyword = c("porn"), geo = c("EG", "SA", "AE","JO", "MA"), time = "today+5-y") 
 

  #combine data for sex and porn searches by merging D2 and D1
#search values are stored in the interest over time tibble: here is some information from google on what that represents:
# Numbers represent search interest relative to the highest point on the chart for the given region and time. A value of 100 is the peak popularity for the term. A value of 50 means that the term is half as popular. A score of 0 means there was not enough data for this term.

D2_interest <- D2$interest_over_time %>% 
  select(hits, date) %>% 
  transmute(hits.porn = hits, date = date)
  

D1_interest <- D1$interest_over_time %>% 
  mutate(hits.sex = hits) %>% 
  full_join(D2_interest, by = "date") %>% 
  mutate(sum = (hits + hits.porn)/2) %>% 
  select(-hits)


#download world data to see if theres a world influence, the default is world data unless you change something
world <- gtrends(keyword = "sex", time = "today+5-y")
world2 <- gtrends(keyword = "porn", time = "today+5-y")

world2 <- world2$interest_over_time %>% 
  select(hits, date) %>% 
  transmute(hits_sex = hits, date = date)

world_interest <- world$interest_over_time %>% 
  full_join(world2, by = "date") %>% 
  mutate(sum.porn = (hits + hits_sex)/2)


#load the data set I made with dates of ramadan and major holidays

ramadan_dates <- read_excel("ramadan_dates.xlsx")


```


The table below shows related queries for searches in the category of sex and porn over Ramadan. Two demonstrate the nature of the searches I display the top 10 related search values. Warning, this includes graphic content.
According to the google trends website, scoring is on a relative scale where a value of 100 is the most commonly searched query, 50 is a query searched half as often as the most popular query, and so on.
  
```{r, cache = TRUE, echo = FALSE, message = FALSE, warning= FALSE}
#showing/determining high volume porn searches 


#justify that I'm picking the right terms (warning explicit content) - since I'm focused with change over time - its not critical that I isolate all the relevant terms but just that they indeed be pornography serach terms  and that they capture a high level of the variation over time
#related queries captures the following: 
# Users searching for your term also searched for these queries. You can sort by the following metrics:
# * Top - The most popular search queries. Scoring is on a relative scale where a value of 100 is the most commonly searched query, 50 is a query searched half as often as the most popular query, and so on.
  
D1$related_queries %>% 
     select(subject, value) %>% 
      slice(1:10) %>% 
     kable(caption = "A Table of Related Queries", col.names = c("Correlation Score", "Value"))

D2$related_queries %>% 
  select(subject, value) %>% 
  slice(1:10) %>% 
  kable(caption = "A Table of Related Queries", col.names = c("Correlation Score", "Value"))



```


```{r, cache = TRUE, include = FALSE, echo = FALSE, message = FALSE, warning= FALSE}


#I have a problem: the gtrends data set does not indicate the presence or absence of Ramadan. I have to pull that info from a different data set I have called ramadan_holiday
#My google trends data set (D1_interest) includes ramadan search values for a whole week 
#manipulate data set to add all days of the week 
D1_interest$date1 = as.Date(D1_interest$date) + 1 
D1_interest$date2 = as.Date(D1_interest$date) + 2 
D1_interest$date3 = as.Date(D1_interest$date) + 3 
D1_interest$date4 = as.Date(D1_interest$date) + 4 
D1_interest$date5 = as.Date(D1_interest$date) + 5 
D1_interest$date6 = as.Date(D1_interest$date) + 6 

D1_interest$year <- substring(D1_interest$date,1,4)


#For loop to create (1) a "days_in_ram" variable ->  the number of days in a given week with ramadan present and also (2) "in_ram" variable -> (0 or 1) whether or not ramadan is present in that week
#first iterate over a week in a given year in the D1_interests data set to see if there are any matches for Ramadan occuring
#count the number of days of a given week in teh D1_interest$date variable which overlap with ramadan
#create a binary variable to code 1 if a week includes more than 3 days of ramadan. 

for (i in 1:length(D1_interest$date)) {
  D1_interest[i, "days_in_ram"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (D1_interest[i, j] >= ramadan_dates[ramadan_dates$year==   D1_interest[i, "year"]   &  ramadan_dates$Holiday == "Ramadan" , ]$start  ) & (D1_interest[i, j] <= ramadan_dates[ramadan_dates$year== D1_interest[i,"year"] & ramadan_dates$Holiday == "Ramadan" ,]$end  ) ) {
        D1_interest[i, "days_in_ram"] =   D1_interest[i, "days_in_ram"]  + 1
    }
  }
  
  if (D1_interest[i, "days_in_ram"] > 2){
      D1_interest[i,"in_ram"] = 1
  } else{
      D1_interest[i,"in_ram"] = 0
  }
  
  
}

#Thank you to Eric Wasserman Harvard 2019 Dunster House for helping me conceptualize how best to approach the coding problem above!


#my next step in data manipulation before running a regression will be to add an additional variable for year so that I can control #for that. 
#I also may go back up (before doing the ramadan stuff) and create a combined variable of porn searches called porn which is the #average of the high volume porn searches I've found 


#repeat the ramadan iteration but this time for celebratory holidays

#first I'll manipulate the ramadan_dates to code "celebratory holiday for Eid""


#code variable for celebratory holidays, same method as ramadan 


for (i in 1:length(D1_interest$date)) {
  D1_interest[i, "days_in_eid"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (D1_interest[i, j] >= ramadan_dates[ramadan_dates$year==   D1_interest[i, "year"]   &  ramadan_dates$Holiday ==  "Eid al-Fitr" , ]$start  ) & (D1_interest[i, j] <=  ramadan_dates[ramadan_dates$year== D1_interest[i,"year"] & ramadan_dates$Holiday ==  "Eid al-Fitr" ,]$end  ) ) {
        D1_interest[i, "days_in_eid"] =   D1_interest[i, "days_in_eid"]  + 1
    }
  }

}


for (i in 1:length(D1_interest$date)) {
  D1_interest[i, "days_in_eida"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (D1_interest[i, j] >= ramadan_dates[ramadan_dates$year==   D1_interest[i, "year"]   &  ramadan_dates$Holiday ==  "Eid-al-adha" , ]$start  ) & (D1_interest[i, j] <=  ramadan_dates[ramadan_dates$year== D1_interest[i,"year"] & ramadan_dates$Holiday ==  "Eid-al-adha" ,]$end  ) ) {
        D1_interest[i, "days_in_eida"] =   D1_interest[i, "days_in_eid"]  + 1
    }
  }

  
}
 

#write an rds file to graph the data 
write_rds(D1_interest, "D1_interest.rds")


```




```{r, cache = TRUE, include = FALSE, echo = FALSE, message = FALSE, warning= FALSE}

#repeat the above step but for WORLD data to test if there's a global impact



#I have a problem: the gtrends data set does not indicate the presence or absence of Ramadan. I have to pull that info from a different data set I have called ramadan_holiday
#My google trends data set (D1_interest) includes ramadan search values for a whole week 
#manipulate data set to add all days of the week 
world_interest$date1 = as.Date(world_interest$date) + 1 
world_interest$date2 = as.Date(world_interest$date) + 2 
world_interest$date3 = as.Date(world_interest$date) + 3 
world_interest$date4 = as.Date(world_interest$date) + 4 
world_interest$date5 = as.Date(world_interest$date) + 5 
world_interest$date6 = as.Date(world_interest$date) + 6 

world_interest$year <- substring(world_interest$date,1,4)


#For loop to create (1) a "days_in_ram" variable ->  the number of days in a given week with ramadan present and also (2) "in_ram" variable -> (0 or 1) whether or not ramadan is present in that week
#first iterate over a week in a given year in the D1_interests data set to see if there are any matches for Ramadan occuring
#count the number of days of a given week in teh D1_interest$date variable which overlap with ramadan
#create a binary variable to code 1 if a week includes more than 3 days of ramadan. 

for (i in 1:length(world_interest$date)) {
  world_interest[i, "days_in_ram"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (world_interest[i, j] > ramadan_dates[ramadan_dates$year==   world_interest[i, "year"]   &  ramadan_dates$Holiday == "Ramadan" , ]$start  ) & (world_interest[i, j] < ramadan_dates[ramadan_dates$year== world_interest[i,"year"] & ramadan_dates$Holiday == "Ramadan" ,]$end  ) ) {
        world_interest[i, "days_in_ram"] =   world_interest[i, "days_in_ram"]  + 1
    }
  }
  
  if (world_interest[i, "days_in_ram"] > 2){
      world_interest[i,"in_ram"] = 1
  } else{
      world_interest[i,"in_ram"] = 0
  }
  
  
}

#same code as above - Eid al-fitr: days_in_eid

for (i in 1:length(world_interest$date)) {
  world_interest[i, "days_in_eid"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (D1_interest[i, j] >= ramadan_dates[ramadan_dates$year==   D1_interest[i, "year"]   &  ramadan_dates$Holiday ==  "Eid al-Fitr" , ]$start  ) & (D1_interest[i, j] <=  ramadan_dates[ramadan_dates$year== world_interest[i,"year"] & ramadan_dates$Holiday ==  "Eid al-Fitr" ,]$end  ) ) {
        world_interest[i, "days_in_eid"] =   world_interest[i, "days_in_eid"]  + 1
    }
  }

}

#same code as above - Eid al-ahda: days_in_eida


for (i in 1:length(world_interest$date)) {
  world_interest[i, "days_in_eida"] = 0 
  for( j in c("date" , "date1", "date2" , "date3", "date4", "date5", "date6")){
    if ( (world_interest[i, j] >= ramadan_dates[ramadan_dates$year==   D1_interest[i, "year"]   &  ramadan_dates$Holiday ==  "Eid-al-adha" , ]$start  ) & (D1_interest[i, j] <=  ramadan_dates[ramadan_dates$year== world_interest[i,"year"] & ramadan_dates$Holiday ==  "Eid-al-adha" ,]$end  ) ) {
        world_interest[i, "days_in_eida"] =   world_interest[i, "days_in_eid"]  + 1
    }
  }

  
}


```



This table of descriptive statistics gives an overview of the data. As indicated, there are 6500 observations. Understanding values for sex and porn searches:
According to the google trends website, numbers represent search interest relative to the highest point on the chart for the given region and time. A value of 100 is the peak popularity for the term. A value of 50 means that the term is half as popular. A score of 0 means there was not enough data for this term. 
```{r, include = FALSE, echo = FALSE, message = FALSE, warning= FALSE, results = "asis", cache = TRUE}
#regression analysis


#displaying summary statistics

#I realize I don't like the display for this approach quite as much 
# trends = gtrends(keyword = c("sex"), geo = c("EG", "SA", "AE","JO", "MA"), time = "today+5-y")
# #select only interst over time 
# time_trend=trends$interest_over_time %>% 
#   select(-keyword, -gprop)
# head(time_trend)

#I edit here with type = "text" but will switch to type = html for print out
des_table <- D1_interest %>% 
  select(-days_in_ram, -days_in_eid, -days_in_eida, -in_ram) %>% 
  stargazer(type = "html", title="Descriptive statistics", digits=1, flip = TRUE, summary.stat = c("n", "mean", "sd", "max"), summary.logical= FALSE)

des_table
# #CODE FOR SELECTIVE DESCRIPTIVE Stats
#  stargazer(mydata[c("mpg","hp","data")], type = "text",
#  title="Descriptive statistics/selected variables", digits=1, out="table2.txt", flip=TRUE,
#  covariate.labels=c("Miles/(US)gallon","Gross horsepower","Rear axle ratio"))

```



```{r, include = FALSE}
#regression analysis - putting togethor the regressions


#both year and country controls, switching between in_ram and days_in_ram
m5 <- lm(sum ~ in_ram + geo + year, data=D1_interest)
m6 <- lm(sum ~ days_in_ram + geo + year, data=D1_interest)


#I'm having an issue where the table prints the names of all the countries 

#Make a regression table
#first regression without year or country controls
ma <- lm(sum ~ days_in_ram, data=D1_interest)


#adding country controls
mb <- lm(sum ~ in_ram, data=D1_interest)

#year and country controls dont make a difference in p values, sd, or coeff so I'm back to removing them - probably because data set is already normalized for year and country
m1 <- lm(sum ~ in_ram + days_in_eid, data=D1_interest)
m2 <- lm(sum ~ days_in_ram + days_in_eid, data=D1_interest)



 # covariate.labels=c("Gross horsepower","Rear axle ratio","Four foward gears",
 # "Five forward gears","Type of transmission (manual=1)")





#global data -  sig impact detected
m3 <- lm(hits ~ days_in_ram, data=world_interest)
m4 <-  lm(hits ~ in_ram, data=world_interest)


```


This regression table output demonstrates how Ramadan causes a sigificant decrease in sex and porn related searches in five muslim majority countries. It also indicates how the presence of a feasting holiday, Eid-al-Futr, which occurs in the week following Ramadan, results in an increase in related search values. The regression is run on sex and porn search values aggregated on a weekly basis. 

"Days in Ramadan" is a continuous variable with values zero throuhg seven, designating the number of days in a a given week which include. "Presence of Ramadan" is a binary variable with values of one or zero based on the presence of absence of Ramadan.

"Days in Eid" is a continuous variable which counts the number of days of Eid al-Futr which occur in a given week. Eid al-Futr is a feasting holiday which occurs immediately following Ramadan. 
```{r, echo = FALSE, message = FALSE, warning= FALSE, results = "asis"}
#use results = asis in the caption to make sure the table prints properly


#reviewing this final regression - I realize I should also look into including a binary variable for the presence of Eid, given that that seems to yeild a more significant result. 
stargazer(ma, mb, m1, m2, summary = FALSE, type = "html", title = "Changes in Sex and Porn Related Search Values Over Ramadan in 5 Muslim-Majority Countries", dep.var.labels = "Mean values for 'sex' and 'porn' hits",  covariate.labels = c("Days in Ram", "Presence of Ram (0 or 1)", "Days in Eid"))



```








It's important to acknowledge that the population covered in my study are those people who access pornography searches not through a proxy site and it is likely that this population would differ somewhat from those who use a proxy site and are not found on google. thus my sample size is not representative of the population as a whole 
